---
title: "Introdunction to Knapsacked"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introdunction to Knapsacked}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::install_github("wountoto/Lab6_R", subdir = "knapsacked", build_vignettes = TRUE)
library(knapsacked)
RNGversion(min(as.character(getRversion()),"3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```


Implementation of Brute force search

```{r}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```

Question: How much time does it takes to run the algorithm for n = 16 objects? 
```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
```

####
Implementation of Dynamic Programming 
```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
```
Question: How much time does it takes to run the algorithm for n = 500 objects?
```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```


###
Implementation of Greedy Heuristic
```{r}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
```
Question: How much time does it takes to run the algorithm for n = 1000000 objects?
```{r}
n <- 1000000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 15000))
```


Question: What performance gain could you get by trying to improving your code?

- We replaced 2 if-else with 1 if-else in the brute_force_knapsack code (line 13). 
- We changed from using For loops to sapply. 
- The creation of clusters function in parallel processing takes time and this could not be improved 
- In the brute_force_knapsack code, we changed from using the "which" function to the "==" operator which removed the      redundant 0s. (line 9)
- the greedy_knaspsack code runs very fast and there was nothing needed to improve there. 

All of the above helped slightly improve the system.time()


