---
title: "Introdunction to Knapsacked"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introdunction to Knapsacked}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(knapsacked)
RNGversion(min(as.character(getRversion()),"3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```


Implementation of Brute force search

```{r}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```

Question: How much time does it takes to run the algorithm for n = 16 objects? 
```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
```

####
Implementation of Dynamic Programming 
```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
```
Question: How much time does it takes to run the algorithm for n = 500 objects?
```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```


###
Implementation of Greedy Heuristic
```{r}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
```
Question: How much time does it takes to run the algorithm for n = 1000000 objects?
```{r}
n2 <- 1000000
knapsack_objects2 <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n2, 0, 10000)
)
system.time(greedy_knapsack(x = knapsack_objects2[1:1000000,], W = 15000))
```


Question: What performance gain could you get by trying to improving your code?

- We replaced 2 if-else with 1 if-else in the brute_force_knapsack code (line 13). 
- We changed from using For loops to sapply. 
- The creation of clusters function in parallel processing takes time and this could not be improved 
- In the brute_force_knapsack code, we changed from using the "which" function to the "==" operator which removed the      redundant 0s. (line 9)
- the greedy_knaspsack code runs very fast and there was nothing needed to improve there. 

All of the above helped slightly improve the system.time()



```{r,warning=FALSE, message=FALSE}


profvis::profvis(brute_force_knapsack(x = knapsack_objects[1:20,], W = 3500))

profvis::profvis(brute_force_knapsack(x = knapsack_objects[1:20,], W = 3500, parallel=TRUE))
```

For our computer its faster not to do the calculations on multiple cores as the function to split it into clusters takes most of the time when not using more than 16 rows from the knapsack object. If that process would go faster then the parallelize brute force search would go faster than on one core. 

But when trying the functions on 20 rows then the parallelize function makes the computation faster(7 seconds vs 8.5 on our computer). 
